---
title: "DDP Using Plotly"
author: "Patrick Brooks"
date: "4/15/2020"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plotly)
library(dplyr)

```

# Project Purpose

The United States Centers for Disease Control (CDC) provides a simple CSV file 
of reported [COVID-19](https://www.cdc.gov/coronavirus/2019-ncov/cases-updates/cases-in-us.html)  cases.  The data table contains the state, recorded cases, the state CDC page.  This exercise will use Leaflet to produce an interactive map of this data.  
The code used in this exercise is based in part on a [Plotly Choropleth example](https://plotly.com/r/choropleth-maps/).  

# Methodology
The CDC data contains several US territories not covered by the Plotly map.  The CDC data was
manually cleaned for expediency.  Also a two character code was added to the data file for
Plotly to recognise the state data. 

* A simple "Blues" pallet was used to color code the states based upon the reported cases.  
* A hover varialbe was added and the user can mouse over a state and see cases and the State's CDC site.  
* A legend was added for a macro understanding of the cases reported.  

```{r CDC_Data, echo= FALSE}
# Create Dataframe
d_states = data.frame(readxl::read_xlsx("W3States Reporting Cases of COVID-19 to CDC.xlsx"))


# Create hover text
d_states$hover <- with(d_states, paste( Jurisdiction, '<br>', "Cases", Cases.Reported,'<br>',
                        URL))
# Make state borders white
borders <- list(color = toRGB("red"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = FALSE,
  lakecolor = toRGB('white')
)

l_us = plot_ly(z = ~d_states$Cases.Reported, text = ~d_states$hover, locations =
        ~d_states$code, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = d_states$Cases.Reported, colors = 'Blues', marker = list(line = borders)) %>%
  layout(title = 'US COVID19 cases 04/10/2020', geo = map_options)

l_us
```

# Summary & code listing

This project demonstrates that creating simple interactive spacial maps can be accomplished
with a a little creative effor.  Below is the code that generated the graphic.


```{r code_inclusion, ref.label=knitr::all_labels(), echo = TRUE, eval = FALSE}

```


